---
title: "Errata for *Conceptual Replication of Four Key Findings about Factual Corrections and Misinformation during the 2020 US Election*"
format:
  pdf:
    output-file: coppock_etal_2023_errata.pdf
    toc: false
    number-sections: false
    geometry: margin=1in
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(here)
here::i_am("errata.qmd")

gt <- read_csv(
  here::here("ground_truth", "coppock_etal_2023_ground_truth.csv"),
  col_types = cols(value_paper = col_character(), .default = col_guess())
)

value <- function(id, column = "value_rewrite") {
  row <- gt[!is.na(gt$claim_id) & gt$claim_id == id, ]
  stopifnot(nrow(row) == 1)
  row[[column]]
}

number_word <- function(x) {
  words <- c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine",
             "ten", "eleven", "twelve", "thirteen", "fourteen", "fifteen", "sixteen",
             "seventeen", "eighteen", "nineteen", "twenty")
  words[as.integer(x)]
}

respondents <- format(as.numeric(value("art_intro_total_n")), big.mark = ",")
significant_misinformation <- number_word(value("res_misinfo_sig_count"))

main_claims <- read_csv(here::here("maintained", "output", "text_main_claims.csv"),
                        show_col_types = FALSE)

main <- function(label) {
  row <- main_claims[main_claims$claim == label, ]
  stopifnot(nrow(row) == 1)
  sprintf("%.1f", row$value)
}

persist_w2 <- main("Pooled Wave 2 to Wave 1 ratio, covariate adjusted")
persist_w3 <- main("Pooled Wave 3 to Wave 1 ratio, covariate adjusted")

# The appendix's own printed ratio rows, read out of the transcription of the
# published appendix rather than reconstructed from the reproduction.
published_cells <- read_csv(here::here("ground_truth", "published_appendix_values.csv"),
                            show_col_types = FALSE)

published_ratio <- function(table_number) {
  row <- published_cells |>
    filter(appendix_table == table_number, row_label == "Meta-analysis Meta-analysis ratio yes")
  stopifnot(nrow(row) == 1)
  sprintf("%.2f", row$estimate)
}

appendix_ratio_w2 <- published_ratio(5)
appendix_ratio_w3 <- published_ratio(7)
```

```{r entries}
# THE ERRATA SPINE. Every entry is defined once, here, and rendered from here: into this
# document, and into whatever else needs it, which reads the errata_entries.csv written at
# the bottom of this file rather than keeping a second hand-typed copy.
#
# [[...]] marks the span that changes. Each renderer supplies its own markup for it: bold
# here, \was{} in an edition. Nothing else in a field is markup, so the same string can be
# set by either. Entries 3 and 4 correct several passages at once, so published and
# corrected carry one block per passage, separated by a blank line.
#
# Numbering is the published note's and is APPEND-ONLY: an entry can already have been
# cited, so a later finding is added at the end and never interleaved.
entries <- tribble(
  ~entry, ~class, ~source, ~form, ~title, ~location, ~published, ~corrected, ~note,

  1, "quantity", "pipeline", "full",
  "The reported total sample size",
  "published, introduction",
  "To study fact-checking during the 2020 election season, we conducted eight preregistered panel experiments (total [[N = 17,681]]).",
  str_glue("To study fact-checking during the 2020 election season, we conducted eight preregistered panel experiments (total [[N = {respondents}]])."),
  str_glue(
    "The article's own appendix Table 1 reports the eight panel sizes as 2,321, 2,090, ",
    "2,059, 2,390, 2,582, 2,200, 1,599 and 2,388, which sum to {respondents}, and the ",
    "deposited respondent data hold exactly that many."),

  2, "quantity", "pipeline", "full",
  "The count of experiments in which misinformation reduced accuracy",
  "published, results",
  "Overall, exposure to the misinformation significantly decreased accuracy in [[twelve]] out of the twenty-four opportunities.",
  str_glue("Overall, exposure to the misinformation significantly decreased accuracy in [[{significant_misinformation}]] out of the twenty-four opportunities."),
  str_glue(
    "Appendix Table 1 prints all {significant_misinformation} in its unadjusted rows, and ",
    "the deposited estimates and the reproduction agree on every one of them."),

  3, "float", "pipeline", "full",
  "Two appendix floats carry the same number",
  "published, appendix",
  str_c("[[Table 1:]] Sample composition by panel.",
        "\n\n",
        "[[Table 1:]] Average treatment effects at Wave 1 among all subjects."),
  "the sample composition table on appendix page 3 and the Wave 1 average treatment effect table on appendix page 15 are two different floats, and both are captioned [[Table 1]]. The regression tables that follow are numbered 1 through 7 and the two tables of appendix section 7 are numbered 8 and 9, so the appendix's table numbering runs 1, 1, 2, 3, 4, 5, 6, 7, 8, 9. A reader citing \"appendix Table 1\" cannot be understood.",
  "",

  4, "quantity", "pipeline", "full",
  "The persistence percentages in the main text were not recomputed when the analysis was revised",
  "published, main text, four sentences",
  str_c(
    "We show that [[66 per cent]] of the initial effect of fact-checks on factual beliefs is still detectable one week after initial exposure, with [[50 percent]] detectable after more than two weeks.",
    "\n\n",
    "The effects of fact-checks observed immediately after treatment dissipate somewhat from Wave 1 to Wave 2, on average, at [[66.4 per cent]] of the initial magnitude.",
    "\n\n",
    "On average, the effect in Wave 3 is [[50 per cent]] the magnitude of the original effect, though the smaller number of issues and subjects increases our uncertainty.",
    "\n\n",
    "The effects of fact-checks persisted at [[66 per cent]] the original magnitude after one week and at [[50 per cent]] after more than two weeks."),
  str_c(
    str_glue("We show that [[{persist_w2} per cent]] of the initial effect of fact-checks on factual beliefs is still detectable one week after initial exposure, with [[{persist_w3} percent]] detectable after more than two weeks."),
    "\n\n",
    str_glue("The effects of fact-checks observed immediately after treatment dissipate somewhat from Wave 1 to Wave 2, on average, at [[{persist_w2} per cent]] of the initial magnitude."),
    "\n\n",
    str_glue("On average, the effect in Wave 3 is [[{persist_w3} per cent]] the magnitude of the original effect, though the smaller number of issues and subjects increases our uncertainty."),
    "\n\n",
    str_glue("The effects of fact-checks persisted at [[{persist_w2} per cent]] the original magnitude after one week and at [[{persist_w3} per cent]] after more than two weeks.")),
  str_glue(
    "The Wave 3 correction is larger than the change of pooling alone would make it. The ",
    "deposited three-wave models fitted with covariates regress the wrong outcomes, so the ",
    "ratio behind appendix Table 7's {appendix_ratio_w3} instruments the Wave 2 outcome ",
    "rather than the Wave 3 outcome. Refitted on Wave 3, the random-effects pool is ",
    "{persist_w3} per cent with covariates and ",
    "{main('Pooled Wave 3 to Wave 1 ratio, unadjusted')} per cent without them.",
    "\n\n",
    "One caveat the correction does not remove. A random-effects pool is still a ",
    "precision-weighted average: it weights each fact-check by how precisely that ",
    "fact-check's ratio was measured, not by how much of the population of fact-checks it ",
    "stands for. The corrected percentages are therefore still not quite the quantity the ",
    "sentences describe, which is how much of a typical fact-check's effect survives a week. ",
    "They are the figures the article should have reported, and they are the ones a reader ",
    "can check against the appendix; treating them as an estimate of the population average ",
    "asks more of them than a precision-weighted average can give.")
) |>
  mutate(across(c(title, published, corrected, note), as.character))

stopifnot(nrow(entries) == max(entries$entry), !anyDuplicated(entries$entry))

# The spine's markup, resolved for this document. Another renderer resolves it differently.
bold <- function(x) str_replace_all(x, "\\[\\[(.*?)\\]\\]", "**\\1**")
blocks <- function(x) str_split_1(x, "\n\n")

# A heading is only a heading when a blank line precedes it, which is why every emitted
# entry opens with one. Where an entry corrects several passages the blocks pair off in
# order; entry 3's correction is one explanation of two captions, so the counts differ
# there and the published blocks are set together ahead of it.
emit <- function(n, lead = "") {
  e <- entries |> filter(entry == n)
  cat("\n\n## ", e$entry, ". ", e$title, "\n\n", sep = "")
  if (lead != "") cat(lead, "\n\n", sep = "")
  was <- blocks(e$published)
  now <- blocks(e$corrected)
  if (length(was) == length(now)) {
    walk2(was, now, \(w, n) cat("> ", bold(w), "\n\n**Corrected:** ", bold(n), "\n\n", sep = ""))
  } else {
    walk(was, \(w) cat("> ", bold(w), "\n\n", sep = ""))
    walk(now, \(n) cat("**Corrected:** ", bold(n), "\n\n", sep = ""))
  }
  if (e$note != "") cat(e$note, "\n", sep = "")
}
```

`r str_glue("{str_to_sentence(number_word(nrow(entries)))} corrections to *British Journal of Political Science* article 10.1017/S0007123422000631.")`
None of them changes a conclusion of the article, though the fourth moves four published
percentages by a material amount. Every corrected value below is computed at render time from a
full reproduction of the published analysis, held in the repository
`active-maintenance-aec/coppock_etal_2023`. Percentages are given to one decimal place
throughout, including in sentences where the article gave a whole number, so that every quantity
in a corrected sentence is one the reproduction has verified. Bold marks the values that changed.

```{r entries-1-3, results="asis"}
walk(1:3, emit)
```

```{r entry-4, results="asis"}
emit(4, lead = str_glue(
  "The share of the Wave 1 correction effect that survives to a later wave is the quantity ",
  "the pre-analysis plan defines and the appendix prints in the `ratio` row of each ",
  "persistence table: the per-experiment ratio of the later-wave coefficient to the Wave 1 ",
  "coefficient, pooled across the experiments by meta-analysis. The article reports that ",
  "quantity in four sentences of the main text and again in the appendix, and the two ",
  "disagree. Appendix Tables 5 and 7 print {appendix_ratio_w2} and {appendix_ratio_w3}. The ",
  "main text's 66.4 and 50 are not returned by any pooling, adjustment or sample the ",
  "deposited archive supports.",
  "\n\n",
  "Both figures appear verbatim in versions of this manuscript that predate the analysis ",
  "the article reports, which pooled 23 experiments rather than 24 and whose every cell ",
  "differs from the published ones. They are the earlier analysis's numbers, carried ",
  "forward and never recomputed when the models were revised, rather than the product of a ",
  "different estimator applied to the final data. A reader of the introduction therefore ",
  "takes away a materially different number from a reader of the appendix.",
  "\n\n",
  "The four sentences are corrected below to the random-effects pool of the ",
  "covariate-adjusted ratios computed from the analysis the article actually reports, which ",
  "is the estimator the appendix's own meta-analysis rows use and the specification Figure ",
  "4 plots. Random effects should have been used throughout."))
```

```{r emit-spine}
# The machine-readable spine, written wherever this document is rendered. Anything else
# that needs these entries reads it rather than keeping its own copy, so the two cannot
# drift.
write_csv(entries, here("errata_entries.csv"))
```
