---
title: "Errata for *Conceptual Replication of Four Key Findings about Factual Corrections and Misinformation during the 2020 US Election*"
format:
  pdf:
    output-file: coppock_etal_2023_errata.pdf
    toc: false
    number-sections: false
    geometry: margin=1in
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(here)
here::i_am("errata.qmd")

gt <- read_csv(
  here::here("ground_truth", "coppock_etal_2023_ground_truth.csv"),
  col_types = cols(value_paper = col_character(), .default = col_guess())
)

value <- function(id, column = "value_rewrite") {
  row <- gt[!is.na(gt$claim_id) & gt$claim_id == id, ]
  stopifnot(nrow(row) == 1)
  row[[column]]
}

number_word <- function(x) {
  words <- c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine",
             "ten", "eleven", "twelve", "thirteen", "fourteen", "fifteen", "sixteen",
             "seventeen", "eighteen", "nineteen", "twenty")
  words[as.integer(x)]
}

respondents <- format(as.numeric(value("art_intro_total_n")), big.mark = ",")
significant_misinformation <- number_word(value("res_misinfo_sig_count"))

# Entry 16. The pooled thermometer effects, from the rewrite's own fits, which apply the
# subset the deposit's loop intends. Read here so the corrected sentence and its note carry
# computed values rather than typed ones.
ft <- read_csv(here::here("maintained", "output", "figure_6_ft_targets_meta.csv"),
               show_col_types = FALSE) |>
  filter(lucid_pid_3 == "Overall")
ft_val <- function(which, col) {
  row <- ft[ft$term2 == which, ]
  stopifnot(nrow(row) == 1)
  row[[col]]
}
fc_est <- ft_val("treatmentfactcheck", "estimate")
mi_est <- ft_val("treatmentcontrol", "estimate")
f2 <- function(x) sprintf("%.2f", x)

main_claims <- read_csv(here::here("maintained", "output", "text_main_claims.csv"),
                        show_col_types = FALSE)

main <- function(label) {
  row <- main_claims[main_claims$claim == label, ]
  stopifnot(nrow(row) == 1)
  sprintf("%.1f", row$value)
}

persist_w2 <- main("Pooled Wave 2 to Wave 1 ratio, covariate adjusted")
persist_w3 <- main("Pooled Wave 3 to Wave 1 ratio, covariate adjusted")

# Entry 4's Wave 3 claim, which is a claim about detection and not only about magnitude. The
# six three-wave experiments are read out of the reproduction's own formatted cells, so how
# many of them survive to Wave 3 is counted rather than asserted.
three_wave <- read_csv(here::here("maintained", "output",
                                  "table_a8_persistence_p3_adj.csv"),
                       show_col_types = FALSE) |>
  rename(cell = `Average Effect of Correction versus Control`) |>
  mutate(starred = str_detect(cell, fixed("*")))

w3_issues <- three_wave |> filter(wave == "w3", topic_short != "Meta-analysis")
w3_n <- nrow(w3_issues)
w3_sig <- sum(w3_issues$starred)
w3_survivor <- w3_issues$topic_short[w3_issues$starred]
w1_sig <- sum(three_wave$starred[three_wave$wave == "w1" &
                                   three_wave$topic_short != "Meta-analysis"])

pooled_cell <- function(w) {
  cell <- three_wave$cell[three_wave$wave == w &
                            three_wave$topic_short == "Meta-analysis"]
  stopifnot(length(cell) == 1)
  cell
}
w3_pooled <- pooled_cell("w3")
w3_ratio_pooled <- pooled_cell("ratio")
stopifnot(w3_sig == 1, !str_detect(w3_pooled, fixed("*")),
          !str_detect(w3_ratio_pooled, fixed("*")))

# The appendix's own printed ratio rows, read out of the transcription of the
# published appendix rather than reconstructed from the reproduction.
published_cells <- read_csv(here::here("ground_truth", "published_appendix_values.csv"),
                            show_col_types = FALSE)

published_ratio <- function(table_number, covariates = "yes") {
  row <- published_cells |>
    filter(appendix_table == table_number,
           row_label == str_c("Meta-analysis Meta-analysis ratio ", covariates))
  stopifnot(nrow(row) == 1)
  sprintf("%.2f", row$estimate)
}

appendix_ratio_w2 <- published_ratio(5)
appendix_ratio_w3 <- published_ratio(7)
appendix_ratio_w3_unadj <- published_ratio(6, "no")

# Entries 14 and 15 describe two properties of the appendix's regression tables rather than
# a value in one cell, so they are counted from the transcription of the published tables
# and from the reproduction, never typed.
n_cells <- nrow(published_cells)
n_descending <- sum(published_cells$interval_printed_descending)
n_stars_printed <- sum(published_cells$significance_marker != "" &
                         !is.na(published_cells$significance_marker))
n_stars_should <- as.integer(value("app_reg_stars"))

# Entries 17 and 18, the two three-wave tables. Both are counted from the transcription of
# the published pages and from the reproduction, the same way as 14 and 15. A wave token is
# missing from a row_label exactly where the published page leaves the Wave cell empty, so
# the count of blank cells is a property of the transcription rather than a reading of it.
three_wave_cells <- published_cells |> filter(appendix_table %in% c(6, 7))
n_three_wave_rows <- nrow(three_wave_cells)
n_blank_wave <- sum(!str_detect(three_wave_cells$row_label, "\\b(w1|w3|ratio)\\b"))

# Every cell of appendix Table 7 is wrong where it stands. The ground truth's count of it
# asks a different question, whether a published value appears ANYWHERE in the corrected
# table, and seven do, on rows other than their own: those are the Wave 1 rows, which hold
# the Wave 3 estimate. The remainder hold estimates of an outcome the table does not report.
t7_cells <- as.integer(value("app_reg_t7_cells", "value_paper"))
t7_misplaced <- as.integer(value("app_reg_t7_cells"))
t7_absent <- t7_cells - t7_misplaced

# The one cell entry 18 quotes, from each side. The published side is the transcription; the
# corrected side is the reproduction's own formatted output, which is what the edition sets.
t7_w1_row <- "Presidential winner must be announced election night Panel 6 (MTurk) w1 yes"
t7_published <- three_wave_cells |> filter(appendix_table == 7, row_label == t7_w1_row)
stopifnot(nrow(t7_published) == 1)
t7_published_cell <- sprintf("%.2f (%.2f) [%.2f, %.2f]", t7_published$estimate,
                             t7_published$std_error, t7_published$interval_first,
                             t7_published$interval_second)

t7_corrected_cell <- read_csv(
  here::here("maintained", "output", "table_a8_persistence_p3_adj.csv"),
  show_col_types = FALSE) |>
  filter(topic_short == "Presidential winner must be announced election night",
         wave == "w1") |>
  pull(`Average Effect of Correction versus Control`)
stopifnot(length(t7_corrected_cell) == 1)
```

```{r entries}
# THE ERRATA SPINE. Every entry is defined once, here, and rendered from here: into this
# document, and into whatever else needs it, which reads the errata_entries.csv written at
# the bottom of this file rather than keeping a second hand-typed copy.
#
# [[...]] marks the span that changes. Each renderer supplies its own markup for it: bold
# here, \was{} in an edition. Nothing else in a field is markup, so the same string can be
# set by either. Entries 3 and 4 correct several passages at once, so published and
# corrected carry one block per passage, separated by a blank line.
#
# Numbering is the published note's and is APPEND-ONLY: an entry can already have been
# cited, so a later finding is added at the end and never interleaved.
#
# claim_ids is the semicolon-separated list of ground-truth claim_id values the entry
# corrects, and it is what makes "is this finding published?" a query rather than a reading
# of every note. It is empty where an entry has no ground-truth row, which is normal for a
# bibliographic or typographical entry. An entry correcting a sentence that restates a float
# cell is keyed to the row for the sentence. ground_truth/build_ground_truth.R refuses to
# build if any id here is absent from the ground truth.
entries <- tribble(
  ~entry, ~class, ~source, ~form, ~title, ~location, ~published, ~corrected, ~note, ~claim_ids,

  1, "quantity", "pipeline", "full",
  "The reported total sample size",
  "published, introduction",
  "To study fact-checking during the 2020 election season, we conducted eight preregistered panel experiments (total [[N = 17,681]]).",
  str_glue("To study fact-checking during the 2020 election season, we conducted eight preregistered panel experiments (total [[N = {respondents}]])."),
  str_glue(
    "The article's own appendix Table 1 reports the eight panel sizes as 2,321, 2,090, ",
    "2,059, 2,390, 2,582, 2,200, 1,599 and 2,388, which sum to {respondents}, and the ",
    "deposited respondent data hold exactly that many."),
  "art_intro_total_n",

  2, "quantity", "pipeline", "full",
  "The count of experiments in which misinformation reduced accuracy",
  "published, results",
  "Overall, exposure to the misinformation significantly decreased accuracy in [[twelve]] out of the twenty-four opportunities.",
  str_glue("Overall, exposure to the misinformation significantly decreased accuracy in [[{significant_misinformation}]] out of the twenty-four opportunities."),
  str_glue(
    "Appendix Table 1 prints all {significant_misinformation} in its unadjusted rows, and ",
    "the deposited estimates and the reproduction agree on every one of them."),
  "res_misinfo_sig_count",

  3, "float", "pipeline", "full",
  "Two appendix floats carry the same number",
  "published, appendix",
  str_c("[[Table 1:]] Sample composition by panel.",
        "\n\n",
        "[[Table 1:]] Average treatment effects at Wave 1 among all subjects."),
  "the sample composition table on appendix page 3 and the Wave 1 average treatment effect table on appendix page 15 are two different floats, and both are captioned [[Table 1]]. The regression tables that follow are numbered 1 through 7 and the two tables of appendix section 7 are numbered 8 and 9, so the appendix's table numbering runs 1, 1, 2, 3, 4, 5, 6, 7, 8, 9. A reader citing \"appendix Table 1\" cannot be understood.",
  "",
  "app_duplicate_table_1",

  4, "quantity", "pipeline", "full",
  "The claim that fact-check effects remain detectable after more than two weeks",
  "published, main text, four passages",
  str_c(
    # The mark runs from the comma, not from "with": the corrected text ends
    # the sentence there, so the published comma becomes a full stop and an
    # unmarked change would go onto the remastered page with no colour, rule
    # or flag against it.
    "We show that [[66 per cent]] of the initial effect of fact-checks on factual beliefs is still detectable one week after initial [[exposure, with 50 percent detectable after more than two weeks]].",
    "\n\n",
    "The effects of fact-checks observed immediately after treatment dissipate somewhat from Wave 1 to Wave 2, on average, at [[66.4 per cent]] of the initial magnitude.",
    "\n\n",
    "On average, the effect in Wave 3 is [[50 per cent]] the magnitude of the original effect, though the smaller number of issues and subjects increases our uncertainty.",
    "\n\n",
    "Over time, the effects [[attenuate, but they remain detectable. The effects of fact-checks persisted at 66 per cent the original magnitude after one week and at 50 per cent after more than two weeks]]."),
  str_c(
    str_glue("We show that [[{persist_w2} per cent]] of the initial effect of fact-checks on factual beliefs is still detectable one week after initial [[exposure. More than two weeks after exposure the estimate is {persist_w3} per cent, which this study cannot distinguish from zero]]."),
    "\n\n",
    str_glue("The effects of fact-checks observed immediately after treatment dissipate somewhat from Wave 1 to Wave 2, on average, at [[{persist_w2} per cent]] of the initial magnitude."),
    "\n\n",
    str_glue("On average, the effect in Wave 3 is [[{persist_w3} per cent the magnitude of the original effect, though neither that share nor the pooled Wave 3 effect itself is distinguishable from zero, and only {number_word(w3_sig)} of the {number_word(w3_n)} issues has a Wave 3 effect that is]]."),
    "\n\n",
    str_glue("Over time, the effects [[attenuate. They remain detectable one week after exposure, at {persist_w2} per cent of the original magnitude. The Wave 3 estimate, more than two weeks after exposure, is {persist_w3} per cent of the original magnitude and is not distinguishable from zero]].")),
  str_glue(
    "THIS ENTRY CHANGES A CONCLUSION OF THE ARTICLE, and it is the only one that does. The ",
    "article reports that the effects of fact-checks remain detectable more than two weeks ",
    "after exposure. They do not, in these data. The pooled Wave 3 effect is {w3_pooled} and ",
    "the share of the Wave 1 effect it represents is {w3_ratio_pooled}; neither is ",
    "distinguishable from zero. The one-week claim is unaffected and stands.",
    "\n\n",
    "The magnitude and the detection claim have the same cause, which is entry 18. The ",
    "deposited three-wave models fitted with covariates regress the wrong outcomes, so the ",
    "ratio behind appendix Table 7's {appendix_ratio_w3} instruments the Wave 2 outcome ",
    "rather than the Wave 3 outcome. That cell carried a significance marker and its interval ",
    "excluded zero, and it was the only statistical support anywhere in the article for the ",
    "two-week claim; the unadjusted table beside it already reported {appendix_ratio_w3_unadj} ",
    "with an interval spanning zero, and the two published tables therefore disagreed with ",
    "each other. Refitted on Wave 3, the random-effects pool is {persist_w3} per cent with ",
    "covariates and {main('Pooled Wave 3 to Wave 1 ratio, unadjusted')} per cent without them, ",
    "and neither is significant.",
    "\n\n",
    "The per-issue pattern is what makes the corrected sentence unsupportable rather than ",
    "merely imprecise. Of the {number_word(w3_n)} issues fielded across three waves, ",
    "{number_word(w1_sig)} had a Wave 1 effect distinguishable from zero and ",
    "{number_word(w3_sig)} still has one at Wave 3: \"{w3_survivor}\", whose effect barely ",
    "decays at all. The pooled {persist_w3} per cent is an average over that one issue and ",
    "{number_word(w3_n - w3_sig)} nulls, two of which are wrong-signed. What these data ",
    "support is that one correction survived more than two weeks intact and the rest did not."),
  "art_intro_persist_w2;art_intro_persist_w3;res_persist_w2_precise;res_persist_w3_precise;disc_persist_w2;disc_persist_w3",

  5, "bibliographic", "reference_audit", "brief",
  "Rathje et al. (2022) is printed with one author",
  "published p. 1341",
  "[[Rathje S]] (2022) Letter to the Editors of Psychological Science: Meta-analysis Reveals that Accuracy Nudges Have Little to No Effect for U.S. Conservatives: Regarding Pennycook et al.",
  "Rathje S et al. (2022) Letter to the Editors of Psychological Science: Meta-analysis Reveals that Accuracy Nudges Have Little to No Effect for U.S. Conservatives: Regarding Pennycook et al.",
  paste("Crossref, doi 10.31234/osf.io/945na: Rathje, Roozenbeek, Traberg, Van Bavel and",
        "van der Linden. Four coauthors are missing from the entry, which the reference",
        "list's own style would give as \"Rathje S et al.\" The in-text citation on p. 1330",
        "reads \"Rathje et al. 2022\", so the body of the article has it right."),
  "",

  6, "bibliographic", "reference_audit", "brief",
  "Pennycook and Rand (2019) is printed with the wrong initial",
  "published p. 1340",
  "[[Pennycook D]] and Rand DG (2019) Lazy, not biased",
  "Pennycook G and Rand DG (2019) Lazy, not biased",
  paste("Crossref, doi 10.1016/j.cognition.2018.06.011: Gordon Pennycook and David G. Rand.",
        "The same author is given correctly as \"Pennycook G\" in the 2021 Nature entry two",
        "lines below, and footnote 2 of the article cites \"Pennycook and Rand 2019\", so",
        "only the initial in this entry is wrong. It appears to have been copied from",
        "Rand's."),
  "",

  7, "bibliographic", "reference_audit", "full",
  "Do Facts Matter? is cited with its authors in the wrong order",
  "published pp. 1328 and 1340",
  str_c(
    "Belief in falsehoods may shape political attitudes and behavior in ways that damage democratic accountability ([[Einstein and Hochschild]] 2015; Nyhan 2020)",
    "\n\n",
    "[[Einstein KL and Hochschild J]] (2015) Do Facts Matter? Information and Misinformation in American Politics. Norman, OK: University of Oklahoma Press."),
  str_c(
    "Belief in falsehoods may shape political attitudes and behavior in ways that damage democratic accountability ([[Hochschild and Einstein]] 2015; Nyhan 2020)",
    "\n\n",
    "[[Hochschild JL and Einstein KL]] (2015) Do Facts Matter? Information and Misinformation in American Politics. Norman, OK: University of Oklahoma Press."),
  paste("Library of Congress, LCCN 2014027612: \"Do facts matter? : information and",
        "misinformation in American politics / Jennifer L. Hochschild and Katherine Levine",
        "Einstein\", Norman: University of Oklahoma Press, 2015. Hochschild is the book's",
        "first author. The publisher and the city are as the entry gives them. The entry",
        "keeps the place the published list gave it, under E, because moving an entry is a",
        "re-presentation of the list rather than a correction to it; a reader looking for",
        "it will find it where the article filed it."),
  "",

  8, "bibliographic", "reference_audit", "full",
  "Swire-Thompson is cited under her earlier surname in a 2020 entry",
  "published pp. 1331 and 1341",
  str_c(
    "The use of multiple outcome measures helps mitigate concerns about measurement error ([[Swire, DeGutis, and Lazer]] 2020)",
    "\n\n",
    "[[Swire B, DeGutis J and Lazer D]] (2020) Searching for the Backfire Effect"),
  str_c(
    "The use of multiple outcome measures helps mitigate concerns about measurement error ([[Swire-Thompson, DeGutis, and Lazer]] 2020)",
    "\n\n",
    "[[Swire-Thompson B, DeGutis J and Lazer D]] (2020) Searching for the Backfire Effect"),
  paste("Crossref, doi 10.31234/osf.io/ba2kc, and the published version at",
        "doi 10.1016/j.jarmac.2020.06.006, both give Briony Swire-Thompson. The 2017 Royal",
        "Society Open Science entry above it is correct as \"Swire B\": the name changed",
        "between the two papers. As with entry 7, the entry keeps its published place in",
        "the list."),
  "",

  9, "bibliographic", "reference_audit", "brief",
  "Porter and Wood (2022) is given the title of its preprint",
  "published p. 1341",
  "Porter E and Wood TJ (2022) [[Misinformation on the Facebook news feed: experimental evidence]]. Journal of Politics 84, 1812-1817.",
  "Porter E and Wood TJ (2022) Political misinformation and factual corrections on the Facebook news feed: experimental evidence. Journal of Politics 84, 1812-1817.",
  paste("Crossref, doi 10.1086/719271: \"Political Misinformation and Factual Corrections on",
        "the Facebook News Feed: Experimental Evidence\", The Journal of Politics 84(3),",
        "1812-1817. The volume and the page range are the version of record's; the title is",
        "the OSF preprint's, which the entry also links. The two are different documents and",
        "the entry mixes them."),
  "",

  10, "bibliographic", "reference_audit", "brief",
  "Nyhan (2020) is given a month where its issue number belongs",
  "published p. 1340",
  "Nyhan B (2020) Facts and myths about misperceptions. Journal of Economic Perspectives [[34(August)]], 220-236.",
  "Nyhan B (2020) Facts and myths about misperceptions. Journal of Economic Perspectives 34(3), 220-236.",
  paste("Crossref, doi 10.1257/jep.34.3.220: Journal of Economic Perspectives 34(3),",
        "220-236. The doi the entry itself prints encodes the issue as 3. Every other entry",
        "in the list that gives an issue gives a numeral."),
  "",

  11, "bibliographic", "reference_audit", "full",
  "Dillard is dated a year before the article it cites appeared",
  "published pp. 1328 and 1339",
  str_c(
    "culminated in an insurrection that policymakers have attributed to misinformation about the \"big lie\" of election fraud (Dillard [[2020]]; US House Committee on Energy and Commerce Staff, 2021)",
    "\n\n",
    "Dillard J ([[2020]]) Ocasio-Cortez Reveals Past Sexual Assault, Faults GOP over Riot. Bloomberg."),
  str_c(
    "culminated in an insurrection that policymakers have attributed to misinformation about the \"big lie\" of election fraud (Dillard [[2021]]; US House Committee on Energy and Commerce Staff, 2021)",
    "\n\n",
    "Dillard J ([[2021]]) Ocasio-Cortez Reveals Past Sexual Assault, Faults GOP over Riot. Bloomberg."),
  paste("The Bloomberg article is dated 2 February 2021, which the entry's own URL records",
        "in its path, and it reports the aftermath of the 6 January 2021 attack on the",
        "Capitol. Its author is Jarrell Dillard, so the initial is right. Dated 2020 the",
        "entry describes a report published before the event it reports."),
  "",

  12, "bibliographic", "reference_audit", "brief",
  "Shin and Thorson (2017) carries a capital left over from its title case",
  "published p. 1341",
  "Shin J and Thorson K (2017) Partisan selective sharing: the biased diffusion of fact-checking messages on [[social Media]]. Journal of Communication 67(2), 233-255.",
  "Shin J and Thorson K (2017) Partisan selective sharing: the biased diffusion of fact-checking messages on social media. Journal of Communication 67(2), 233-255.",
  paste("The published title is \"Partisan Selective Sharing: The Biased Diffusion of",
        "Fact-Checking Messages on Social Media\" (doi 10.1111/jcom.12284). The reference",
        "list sets titles in sentence case, and the M of Media is the only capital left",
        "standing from the original."),
  "",

  13, "typographical", "remaster", "brief",
  "A sentence break in the appendix has lost its space",
  "published, appendix p. 8",
  "Figures 4, 5, 6 display the coefficient [[estimates.These]] regressions return p-values below 0.05",
  "Figures 4, 5, 6 display the coefficient estimates. These regressions return p-values below 0.05",
  paste("Found by reading the appendix against its own PDF while preparing the remastered",
        "edition. The two sentences are run together with no space after the full stop."),
  "",

  14, "float", "remaster", "full",
  "Confidence intervals in the appendix regression tables are printed low bound last",
  "published, appendix pp. 15 to 20",
  str_c("12.97 (2.01) [[[16.91, 9.03]]]"),
  str_glue(
    "the seven regression tables print [[{n_descending} of their {n_cells} intervals with the ",
    "bounds transposed]], so that the interval reads from its upper limit to its lower one. ",
    "The cell quoted above, the first in appendix table 1, should read [9.03, 16.91]. Every ",
    "interval whose estimate is negated by the table code is affected and no other is."),
  paste("The deposited script negates an estimate and both of its interval bounds without",
        "reversing them, so a two-sided interval comes out backwards whenever the sign is",
        "flipped. The bounds themselves are right and the reproduction returns the same two",
        "numbers for every affected cell; only their order on the page is wrong. The",
        "remastered edition sets all seven tables from the reproduction, so every interval",
        "in it reads from its lower limit to its upper one."),
  "app_reg_descending",

  15, "float", "remaster", "full",
  "Significance markers in the appendix regression tables were set by comparing strings",
  "published, appendix pp. 15 to 20",
  str_glue("[[{n_stars_printed}]] of the {n_cells} cells in the seven regression tables carry a significance marker."),
  str_glue(
    "[[{n_stars_should}]] of them have a p-value below 0.05. The marker is on the wrong cells: ",
    "\"0.0144\" sorts before \"0.05\" and earns a star, while \"1.28e-10\" sorts after it and does ",
    "not, so the most significant estimates in these tables are among the unstarred ones."),
  paste("The deposited table script reshapes each fit with a function whose identifier",
        "columns omit a character column, which coerces every value in the reshaped frame to",
        "a string; the surviving comparison with 0.05 is then a comparison of two strings",
        "rather than of two numbers. It is deterministic and reproducible: running the",
        "deposit's own script prints the published tables verbatim, star pattern included.",
        "As with entry 14, the remastered edition sets the tables from the reproduction, so",
        "its marker follows the p-value."),
  "app_reg_stars",

  16, "quantity", "pipeline", "full",
  "The attitude effects are attenuated by a filter that does not filter",
  "published pp. 2 and 11",
  # str_c, not paste: paste's separator puts a space on either side of the block
  # break, and a block that begins or ends with one does not match the published
  # page. See the whitespace check below the tribble.
  str_c(
    "the effects of fact-checks and misinformation on subsequent attitudes are ",
    "[[smaller than one-quarter of a point]]",
    "\n\n",
    "each [[smaller than half a point]]"),
  str_glue(
    "the effects of fact-checks and misinformation on subsequent attitudes are ",
    "[[{f2(fc_est)} of a point and {f2(abs(mi_est))} of a point respectively]]",
    "\n\n",
    "[[{f2(fc_est)} and {f2(mi_est)} points]]"),
  str_glue(
    "Both sentences describe the pooled effects on the feeling thermometers of the people ",
    "and institutions the claims are about. The deposit's loop over those targets subsets ",
    "with filter(all_panels_long, fc == fc, topic_short_2 == topic_short_2), where each ",
    "bare name resolves to the column rather than to the loop variable that shadows it, so ",
    "both conditions compare a column with itself and neither subsets anything. Every ",
    "target model is therefore fitted on all eight panels pooled, including respondents ",
    "never shown the claim, which dilutes each estimate toward zero and understates its ",
    "standard error. The loop extracts those two values one row at a time in order to ",
    "subset, so the intent is not in doubt.",
    "\n\n",
    "Fitting the models on the sample the loop intends gives a correction effect of ",
    "{f2(fc_est)} points (SE {f2(ft_val('treatmentfactcheck','std.error'))}) and a ",
    "misinformation effect of {f2(mi_est)} points (SE ",
    "{f2(ft_val('treatmentcontrol','std.error'))}), both significant at the 5 per cent ",
    "level, against published estimates near 0.2. An independent audit prepared for Ethan ",
    "Porter in June 2026 recomputed these from the deposited data and reached the same two ",
    "figures to three decimal places.",
    "\n\n",
    "The article's qualitative claim survives and its magnitude does not. Facts still move ",
    "beliefs far more than they move attitudes, by a factor of roughly thirteen rather than ",
    "the fifty-five the published figures imply. This is the only entry in this note that ",
    "changes a reported effect rather than a misprint."),
  "art_intro_attitudes_quarter;res_attitudes_half",

  17, "float", "remaster", "full",
  "The Wave column is empty on every Wave 3 row of the three-wave tables",
  "published, appendix p. 20",
  str_glue("[[{n_blank_wave}]] of the {n_three_wave_rows} rows of appendix Tables 6 and 7 print nothing in the Wave column."),
  str_glue(
    "every one of them is a [[Wave 3]] row. The edition sets w3 in those cells and returns ",
    "each group of rows to the order w1, w3, ratio."),
  paste("The deposited table script builds the three-wave tables with the two-wave tables'",
        "factor levels, c(\"w1\", \"w2\", \"ratio\"), so every w3 value becomes NA. xtable prints",
        "NA as an empty cell, and the sort on that factor puts the rows carrying it last,",
        "which is also why each group reads w1, then ratio, then an unlabelled row. The same",
        "line is right where it appears earlier in the same file for the two-wave tables,",
        "whose waves those levels are. Table 6's",
        "numbers are unaffected and every one of its cells reproduces. Table 7's are not, for",
        "the reason entry 18 gives."),
  "",

  18, "float", "pipeline", "full",
  "The adjusted three-wave table reports models of the wrong outcomes",
  "published, appendix p. 20",
  str_glue("[[{t7_published_cell}]]"),
  str_glue(
    "the Wave 1 row of appendix Table 7 should read [[{t7_corrected_cell}]]. The cell quoted ",
    "above is that experiment's Wave 3 estimate, printed on its Wave 1 line. ",
    "[[All {t7_cells} cells of the table]] are wrong where they stand: {t7_misplaced} hold an ",
    "estimate that belongs to another row of the same table, and {t7_absent} hold estimates ",
    "of an outcome the table does not report."),
  paste("The deposit's adjusted three-wave block regresses outcome_w3 for both its Wave 1 and",
        "its Wave 2 models and outcome_w2 for its Wave 3 model, and instruments outcome_w2",
        "rather than outcome_w3 in the ratio. The unadjusted block immediately above it pairs",
        "each wave with its own outcome, and so does the covariate-adjusted block for the",
        "conditional effects below it, so this is a copy-and-paste slip rather than a",
        "modelling decision. The two models it leaves untouched say so outright: the Wave 3",
        "model and the ratio carry the two-wave block's outcome and, in the ratio, its whole",
        "covariate string, so the three-wave block is the two-wave block pasted and only",
        "half re-edited. Its other trace on the page is Figure 4, whose bottom-left panel",
        "draws the Wave 1 and the Wave 2 point at the same height because they are the same",
        "estimate. The unadjusted table beside it, Table 6, is unaffected and reproduces in",
        "every cell. **This entry is the reason entry 4 changes a conclusion.** The ratio row",
        "of the published Table 7 carried a significance marker and an interval excluding",
        "zero, and it was the article's only statistical support for the claim that fact-check",
        "effects remain detectable more than two weeks after exposure. Instrumented on the",
        "outcome the table names, the estimate is smaller and its interval spans zero."),
  "app_reg_t7_cells"
) |>
  mutate(across(c(title, published, corrected, note), as.character))

stopifnot(nrow(entries) == max(entries$entry), !anyDuplicated(entries$entry))

# NO BLOCK MAY BEGIN OR END WITH WHITESPACE. A stray space is invisible in this note and
# does real damage in an edition, where the published block is the string matched against
# the published page: a trailing space demands whitespace where the page has a full stop, so
# the match fails and the correction is silently never made, and a leading space is consumed
# by the replacement, welding the corrected text to the word before it. Entry 16 did both on
# 2026-08-12, from a paste() whose separator fell either side of the block break, and the
# edition printed one sentence uncorrected while this note published it as corrected.
whitespace_at_a_block_edge <- function(x) {
  str_detect(x, "(^|\n\n)[ \t]") | str_detect(x, "[ \t](\n\n|$)")
}
stopifnot(!any(whitespace_at_a_block_edge(c(entries$published, entries$corrected))))

# Every id an entry claims to correct must be a real ground-truth claim. The build gate in
# ground_truth/build_ground_truth.R checks the same property from the other side; checking it
# here too means a dangling id cannot survive a render.
gt_ids <- read_csv(here::here("ground_truth", "coppock_etal_2023_ground_truth.csv"),
                   show_col_types = FALSE)$claim_id
cited_ids <- entries$claim_ids |>
  str_split(";") |>
  unlist() |>
  str_trim() |>
  discard(\(x) is.na(x) | x == "")
stopifnot(all(cited_ids %in% gt_ids))

# The spine's markup, resolved for this document. Another renderer resolves it differently.
bold <- function(x) str_replace_all(x, "\\[\\[(.*?)\\]\\]", "**\\1**")
blocks <- function(x) str_split_1(x, "\n\n")

# A heading is only a heading when a blank line precedes it, which is why every emitted
# entry opens with one. Where an entry corrects several passages the blocks pair off in
# order; entry 3's correction is one explanation of two captions, so the counts differ
# there and the published blocks are set together ahead of it.
# Which entries this document has set, so that the check at the foot of the file can refuse
# a spine entry that no section emits. The sections are explicit lists rather than a walk
# over the whole spine, because the order of the note is not the order of the numbering:
# entry 16 is set last of the first sixteen, and 17 and 18 follow it.
emitted <- integer(0)

emit <- function(n, lead = "") {
  e <- entries |> filter(entry == n)
  emitted <<- c(emitted, n)
  cat("\n\n## ", e$entry, ". ", e$title, "\n\n", sep = "")
  if (lead != "") cat(lead, "\n\n", sep = "")
  was <- blocks(e$published)
  now <- blocks(e$corrected)
  if (length(was) == length(now)) {
    walk2(was, now, \(w, n) cat("> ", bold(w), "\n\n**Corrected:** ", bold(n), "\n\n", sep = ""))
  } else {
    walk(was, \(w) cat("> ", bold(w), "\n\n", sep = ""))
    walk(now, \(n) cat("**Corrected:** ", bold(n), "\n\n", sep = ""))
  }
  if (e$note != "") cat(e$note, "\n", sep = "")
}
```

`r str_glue("{str_to_sentence(number_word(nrow(entries)))} corrections to *British Journal of Political Science* article 10.1017/S0007123422000631.")`
**One of them changes a conclusion of the article.** Entry 4 withdraws the claim that the effects
of fact-checks remain detectable more than two weeks after exposure. The pooled Wave 3 effect is
not distinguishable from zero, nor is the share of the Wave 1 effect it represents, and the only
statistical support the article had for the claim was a cell produced by a model of the wrong
outcome, which entry 18 corrects. The one-week finding is unaffected and stands, as does
everything else the article concludes. Of the remaining entries, eight are in the reference list
and the rest correct misprints and appendix floats. Every corrected value
below is computed at render time from a
full reproduction of the published analysis, held in the repository
`active-maintenance-aec/coppock_etal_2023`. Percentages are given to one decimal place
throughout, including in sentences where the article gave a whole number, so that every quantity
in a corrected sentence is one the reproduction has verified. Bold marks the values that changed.

```{r entries-1-3, results="asis"}
walk(1:3, emit)
```

```{r entry-4, results="asis"}
emit(4, lead = str_glue(
  "The share of the Wave 1 correction effect that survives to a later wave is the quantity ",
  "the pre-analysis plan defines and the appendix prints in the `ratio` row of each ",
  "persistence table: the per-experiment ratio of the later-wave coefficient to the Wave 1 ",
  "coefficient, pooled across the experiments by meta-analysis. The article reports that ",
  "quantity in four sentences of the main text and again in the appendix, and the two ",
  "disagree. Appendix Tables 5 and 7 print {appendix_ratio_w2} and {appendix_ratio_w3}. The ",
  "main text's 66.4 and 50 are not returned by any pooling, adjustment or sample the ",
  "deposited archive supports.",
  "\n\n",
  "Both figures appear verbatim in versions of this manuscript that predate the analysis ",
  "the article reports, which pooled 23 experiments rather than 24 and whose every cell ",
  "differs from the published ones. They are the earlier analysis's numbers, carried ",
  "forward and never recomputed when the models were revised, rather than the product of a ",
  "different estimator applied to the final data. A reader of the introduction therefore ",
  "takes away a materially different number from a reader of the appendix.",
  "\n\n",
  "The four sentences are corrected below to the random-effects pool of the ",
  "covariate-adjusted ratios computed from the analysis the article actually reports, which ",
  "is the estimator the appendix's own meta-analysis rows use and the specification Figure ",
  "4 plots. Random effects should have been used throughout."))
```

# The reference list

The entry below corrects the article's reference list. It was found by an audit that sends every printed entry whole to Crossref and checks the authoritative record back into it, and it is verified against the record named in the note. No cited work is missing and no citation in the text points at the wrong work.

```{r reference-entries, results="asis"}
walk(entries$entry[entries$source == "reference_audit"], function(n) {
  e <- entries |> filter(entry == n)
  emitted <<- c(emitted, n)
  cat("\n\n## ", e$entry, ". ", e$title, "\n\nPublished, ",
      str_remove(e$location, "^published "), ":\n\n> ", bold(e$published),
      "\n\nCorrected:\n\n> ", e$corrected, "\n\n", e$note, "\n", sep = "")
})
```

# Found while preparing the remastered edition

The entries below were found by reading every word of the article and its appendix against
the published PDF while a corrected re-typesetting was being prepared, which is a finer sieve
than any pass this repository had run. The last two describe properties of the appendix's
regression tables that the reproduction measures rather than values in a single cell.

```{r remaster-entries, results="asis"}
walk(c(13, 14, 15), emit)
```

# The attitude estimates

The entry below changes a reported effect rather than correcting a misprint, and it is set
out here rather than earlier because the numbering of this note is append-only: an entry
that has been published can already have been cited, so a later finding is added at the end
and no earlier entry moves.

```{r entry-16, results="asis"}
emit(16, lead = str_glue(
  "This note's other entries correct what the article prints. This one corrects what the ",
  "article concludes from a quantity its own code miscomputed, so it is set out at more ",
  "length. The finding is not new to this reproduction: the repository has recorded the ",
  "defect since the rewrite was built, in the reproducibility report rather than here, on ",
  "the reasoning that the fault lay in the deposited code rather than in the article. That ",
  "reasoning was wrong. Where a defect in the code reaches the printed page, a reader is ",
  "misled by the page, and whose mistake it was does not change what the reader takes away."))
```

# The three-wave persistence tables

The two entries below correct appendix Tables 6 and 7, which report the persistence of the correction effect to Wave 3. Both were found by setting those tables from the reproduction rather than reproducing the published pages as images, which is what the remastered edition now does with all seven regression tables: a table that has to be rebuilt cell by cell is read far more closely than a table that is photographed. The first corrects a column of labels the deposit's own script emptied. The second corrects the numbers.

```{r three-wave-entries, results="asis"}
walk(c(17, 18), emit)
```

```{r emit-spine}
# Every entry in the spine is set once by exactly one section above. Without this an entry
# could be added to the spine, counted in the note's own opening sentence, written into the
# csv the edition reads, and never printed here.
stopifnot(setequal(emitted, entries$entry), !anyDuplicated(emitted))

# The machine-readable spine, written wherever this document is rendered. Anything else
# that needs these entries reads it rather than keeping its own copy, so the two cannot
# drift.
write_csv(entries, here("errata_entries.csv"))
```
