---
title: "Maintained reproduction of Coppock, Gross, Porter, Thorson and Wood (2023)"
format:
  gfm:
    output-file: README.md
    toc: true
  pdf:
    output-file: coppock_etal_2023_report.pdf
    toc: true
    number-sections: true
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(here)
library(knitr)
here::i_am("README.qmd")

latex_out <- knitr::is_latex_output()
options(width = 200)

gt <- read_csv(
  here::here("ground_truth", "coppock_etal_2023_ground_truth.csv"),
  col_types = cols(value_paper = col_character(), .default = col_guess())
)
coverage <- read_csv(here::here("ground_truth", "float_coverage.csv"), show_col_types = FALSE)
run_status <- read_csv(here::here("ground_truth", "archive_run_status.csv"), show_col_types = FALSE)
overwrites <- read_csv(here::here("ground_truth", "archive_overwrites.csv"), show_col_types = FALSE)
fit_check <- read_csv(here::here("maintained", "output", "text_archive_fit_check.csv"),
                      show_col_types = FALSE)
main_claims <- read_csv(here::here("maintained", "output", "text_main_claims.csv"),
                        show_col_types = FALSE)
manifest <- read_csv(here::here("original_manifest.csv"), show_col_types = FALSE)
published_cells <- read_csv(here::here("ground_truth", "published_appendix_values.csv"),
                            show_col_types = FALSE)
extraction <- read_csv(here::here("ground_truth", "published_claims.csv"),
                       col_types = cols(value_paper = col_character(),
                                        needs_block = col_logical(),
                                        .default = col_guess()))

# claim_id is never missing in this ground truth, but indexing it with a bare
# logical would return extra NA elements the moment one were, so every lookup
# goes through an accessor that asserts a single row.
value <- function(id, column = "value_rewrite") {
  row <- gt[!is.na(gt$claim_id) & gt$claim_id == id, ]
  stopifnot(nrow(row) == 1)
  row[[column]]
}

pass <- function(name) run_status |> filter(pass == name)

main <- function(label) {
  row <- main_claims[main_claims$claim == label, ]
  stopifnot(nrow(row) == 1)
  sprintf("%.1f", row$value)
}

persistence_estimates <- main_claims$value[main_claims$claim %in% c(
  "Pooled Wave 2 to Wave 1 ratio, covariate adjusted",
  "Pooled Wave 2 to Wave 1 ratio, unadjusted",
  "Pooled Wave 3 to Wave 1 ratio, covariate adjusted",
  "Pooled Wave 3 to Wave 1 ratio, unadjusted",
  "Wave 2 correction effect as a percentage of Wave 1, covariate adjusted",
  "Wave 3 correction effect as a percentage of Wave 1, covariate adjusted"
)]

show_table <- function(x, caption = NULL) {
  if (latex_out) {
    knitr::kable(x, caption = caption, booktabs = TRUE, linesep = "") |>
      kableExtra::kable_styling(latex_options = c("striped", "scale_down"))
  } else {
    knitr::kable(x, caption = caption)
  }
}

figure <- function(stem) {
  extension <- if (latex_out) ".pdf" else ".png"
  knitr::include_graphics(file.path("maintained", "output", paste0(stem, extension)))
}
```

*Drafted by Claude Opus 5 under the supervision of Alex Coppock.*

## What this repository is

This repository re-runs the analysis behind a published article from its deposited data, in
current R, and lays every number the article prints against what that analysis produces. It holds
three things: a script that fetches and verifies the authors' replication archive, a rewrite of
the analysis using current packages, and a ground truth that records, claim by claim, whether the
published number reproduces.

| | |
|---|---|
| Article | Coppock A, Gross K, Porter E, Thorson E and Wood TJ (2023). "Conceptual Replication of Four Key Findings about Factual Corrections and Misinformation during the 2020 US Election: Evidence from Panel-Survey Experiments." *British Journal of Political Science*. <https://doi.org/10.1017/S0007123422000631> |
| Replication archive | <https://doi.org/10.7910/DVN/WQXZUP> |
| Pre-analysis plan | <https://osf.io/2hnv5> |

### Folder layout

```
download_original.R    fetches and verifies the deposited archive
run_all.R              runs everything, in order
original/              the deposited archive (not redistributed; fetched on demand)
original_manifest.csv  every deposited file, its size and its published checksum
maintained/            the rewrite; maintained/output/ holds every number it produces
ground_truth/          the extraction, the comparison and the gates
errata.qmd             corrections to the published article
```

### How to reproduce

Download the repository, open `coppock_etal_2023.Rproj`, and run:

```r
source("run_all.R")
```

`run_all.R` fetches the deposited archive from Harvard Dataverse, verifies every file against its
published checksum and byte size, fits every model, writes every figure and table, runs the
deposited scripts in a scratch copy, rebuilds the ground truth and re-verifies the archive.
Nothing writes into `original/`.

## The paper

Eight panel-survey experiments fielded on Lucid and Mechanical Turk between September and
November 2020, with `r format(as.numeric(value("art_intro_total_n")), big.mark = ",")`
respondents across `r value("res_opportunities")` experiments built on
`r value("art_intro_fact_checks")` distinct PolitiFact fact-checks. Each respondent saw three
topics; for each topic they were assigned to pure control, misinformation, or misinformation
followed by a fact-check. Belief certainty in the false claim is the primary outcome, measured
again after at least a week.

The headline estimates are a meta-analytic misinformation effect of
`r value("res_meta_misinfo")` points and a correction effect of `r value("res_meta_correction")`
points on the 100-point belief certainty scale.

## Does the deposited archive run?

The deposit is fourteen scripts, six data files and thirty-four saved model objects, in a
directory tree of `r nrow(manifest)` files. Every script was run in a scratch copy, twice: once
as the archive ships, and once stripped to data plus code so that a script which passes only
because the deposit ships the object it reads is visible as a failure.

```{r}
#| label: archive-run
#| echo: false
run_status |>
  count(pass, outcome) |>
  pivot_wider(names_from = outcome, values_from = n, values_fill = 0) |>
  show_table(caption = "Deposited scripts by pass and outcome.")
```

Two scripts fail in every pass, for reasons unrelated to the analysis.
`appendix_figure_3.R` asks the graphics device for a font family that is not installed, and
`appendix_figure_9.R` reads `data/clean/all_panels_long.rds`, a path the deposit does not
contain: its copy of that file sits at `data/all_panels_long.rds`.

Stripping the copy to data plus code is what the second pass adds, and it changes the answer:
`r nrow(pass("stripped") |> filter(outcome != "clean"))` of
`r nrow(pass("stripped"))` scripts fail without the deposited model objects, against
`r nrow(pass("as_shipped") |> filter(outcome != "clean"))` as shipped. Every one of the
additional failures is a `readRDS` of an object `fit_all_models.R` builds. Running
`fit_all_models.R` first and then the analysis scripts, which is the third pass in the table
above, leaves `r nrow(pass("stripped_after_fit") |> filter(outcome != "clean"))` failures. Two are
the pair that fail regardless. The third is `figure_5.R`, and it is a finding of its own: it reads
`fitted_models/meta_trait_dic_w1_all_adj`, a deposited file with no extension, while the deposit's
own code writes that object as `meta_trait_dic_w1_all_adj.rds`, which the archive does not
contain. The object survives only as a deposited artifact; nothing in the deposit can regenerate
it under the name the figure reads.

**The deposit writes nothing except model objects.** Grepping the fourteen scripts for
uncommented calls that touch a file returns thirty-four `write_rds()` lines, all in
`fit_all_models.R`, and nothing else: no `ggsave`, no `write_csv`, no `sink`. Every figure is
drawn to the active device and every table is printed to the console as LaTeX. So there is no
deposited artifact to diff against, and a checksum result on `original/` is a statement about the
download rather than about the analysis.

Running the deposit in place would not be harmless. Measured by modification time in a scratch
copy, `fit_all_models.R` overwrites
`r nrow(overwrites |> filter(effect == "overwritten"))` deposited model objects and adds
`r nrow(overwrites |> filter(effect == "added"))` more, and the figure scripts leave an
`Rplots.pdf` behind.

### Do the deposited objects follow from the deposited data?

Every model the deposit saves was refitted from the survey data and compared against the saved
object.

```{r}
#| label: fit-check
#| echo: false
fit_check |>
  summarize(
    objects = n(),
    `estimates agree to 1e-9` = sum(max_abs_difference_estimate < 1e-9, na.rm = TRUE),
    `estimates disagree` = sum(max_abs_difference_estimate >= 1e-9, na.rm = TRUE),
    `cells missing on one side` = sum(cells_missing_on_one_side)
  ) |>
  show_table(caption = "Deposited model objects against a refit from the deposited data.")
```

```{r}
#| label: fit-check-detail
#| echo: false
fit_check |>
  filter(max_abs_difference_estimate >= 1e-9) |>
  select(object, rows_deposited, rows_rewrite,
         estimate = max_abs_difference_estimate,
         archive_specification = max_abs_difference_estimate_archive_spec) |>
  show_table(caption = "The objects where the refit and the deposit disagree, and what the deposit's own specification gives.")
```

The `archive_specification` column is the same comparison run under the deposit's own model
formulas rather than the corrected ones, and where it returns zero the disagreement above it is
entirely the correction. The two thermometer objects are the exception and are discussed under
the errata below.

Two properties of the comparison are worth stating because a single summary number hides both.
The rewrite reverses the confidence interval the deposit prints backwards for every negated
contrast, so a maximum taken over all six numeric columns at once is the width of the widest
interval in the object and says nothing about agreement. And a cell one side computes while the
other returns as missing is invisible to any difference, which is exactly how the political
knowledge estimates move: the two `estimatr` versions disagree about which HC2 standard errors
are estimable, so the pooling drops a different study.

## Errata

Three sentences in the published article are wrong, and they are corrected in
[`coppock_etal_2023_errata.pdf`](coppock_etal_2023_errata.pdf), whose values are computed
at render time from this repository's output. None of them changes a conclusion. In summary: the
reported total sample size is `r "17,681"` where the article's own appendix table sums to
`r format(as.numeric(value("art_intro_total_n")), big.mark = ",")`; the count of experiments in
which misinformation significantly reduced accuracy is given as twelve where the deposited
estimates give `r value("res_misinfo_sig_count")`; and two different appendix floats are both
captioned Table 1.

### Corrections the rewrite makes to the deposited code

Four coding errors in the deposit are corrected in `maintained/`. Each is unambiguous, in the
sense that the code plainly does something other than what the surrounding code says it is doing.

**The thermometer models are fitted on the wrong sample.** The deposit's loop over targets reads

```r
filter(all_panels_long, fc == fc, topic_short_2 == topic_short_2)
```

Inside `filter()` the bare names resolve to the columns, so both conditions compare a column with
itself and neither subsets anything: every target model is fitted on all eight panels pooled,
including respondents who were never shown the claim. The loop extracts `fc` and `topic_short_2`
one row at a time in order to subset, so the intent is not in doubt. Applying the subset costs
one of the twenty-three target rows, because Panel 3 names Barack Obama as a target and never
asked the Barack Obama thermometer; that row is recorded in
`maintained/output/fits/ft_targets_unfittable.csv`.

This moves Figure 6. The published overall labels are
`r value("fig6_overall_treatmentcontrol", "value_paper")` and
`r value("fig6_overall_treatmentfactcheck", "value_paper")`; the corrected estimates are
`r value("fig6_overall_treatmentcontrol")` and `r value("fig6_overall_treatmentfactcheck")`. All
eight of the figure's labels change, and with them two sentences of prose: the introduction's
"smaller than one-quarter of a point" and the Results section's "smaller than half a point" are
both true of the published figure and false of the corrected one.

These stay findings here rather than errata. The published cells reproduce from the deposit
exactly, so what is wrong with them is a matter of method rather than of arithmetic, and
correcting a column of cells the deposit reproduces exactly is a different act from correcting a
misstated number. The substantive claim is untouched either way: a correction effect of
`r value("fig6_overall_treatmentfactcheck")` points on a 100-point feeling thermometer is as
close to nothing as `r value("fig6_overall_treatmentfactcheck", "value_paper")` is.

**The adjusted three-wave models regress the wrong outcomes.** In the deposit,
`ates_w1_p3_adj` and `ates_w2_p3_adj` both regress `outcome_w3`, `ates_w3_p3_adj` regresses
`outcome_w2`, and `iv_p3_adj` instruments `outcome_w2`. The unadjusted block immediately above
pairs each wave with its own outcome, and so does the covariate-adjusted conditional-effect block
below, so this is a copy-and-paste slip. Two published artifacts show it. Appendix Table 7's `w1`
row holds the wave 3 estimate and its unlabelled row holds the wave 2 estimate, which is why
`r value("app_reg_t7_cells")` of its `r value("app_reg_t7_cells", "value_paper")` cells
reproduce where the other six regression tables reproduce completely. And Figure 4's bottom-left
panel draws its Wave 1 and Wave 2 points at the same height, because they are the same estimate.

**Every negated confidence interval prints backwards.** The deposit's `filter_and_flip()` negates
the estimate and both interval bounds for the misinformation contrast without reversing their
order, so those cells print as `[upper, lower]`.
`r value("app_reg_descending", "value_paper")` of the
`r sum(coverage$printed_numbers[str_starts(coverage$float, "Appendix regression table")]) / 4`
published appendix cells are printed this way. The interval itself is right; only the order is
wrong. The rewrite swaps the bounds back.

**The significance column of the appendix regression tables is not a comparison of numbers.** The
deposit's table script reshapes each fit with `reshape2::melt`, and where a fit carries a
character column outside `id.vars` every melted value becomes a string. The surviving
`if_else(p.value < 0.05, "* ", " ")` then compares two strings, so `"0.0144"` sorts before
`"0.05"` and earns a star while `"1.28e-10"` sorts after it and does not. The effect is that the
most significant estimates in the table are the ones printed without a marker: the published
tables carry `r value("app_reg_stars", "value_paper")` stars where
`r value("app_reg_stars")` cells have p < 0.05. This is deterministic, it is visible on the page
once you know to look for it, and it is a property of the presentation rather than of any
estimate, so it stays a finding here rather than an erratum.

### The persistence percentages reproduce under no expression

The article states three times that fact-check effects persist "at 66 per cent" of their original
magnitude after one week, once at the sharper "66.4 per cent", and "at 50 per cent" after more
than two weeks. Neither number is produced by anything in the deposit or in the rewrite.

The quantity the pre-analysis plan defines, and the one the appendix's own persistence tables
print in their `ratio` rows, is the per-experiment ratio of the later-wave coefficient to the
Wave 1 coefficient, pooled by random-effects meta-analysis. That gives
`r value("res_persist_w2_precise")` per cent at Wave 2 and `r value("res_persist_w3_precise")`
per cent at Wave 3 with covariates, and `r main("Pooled Wave 2 to Wave 1 ratio, unadjusted")` and
`r main("Pooled Wave 3 to Wave 1 ratio, unadjusted")` per cent without them. The ratio of the
pooled Wave 2 effect to the pooled Wave 1 effect gives
`r main("Wave 2 correction effect as a percentage of Wave 1, covariate adjusted")` per cent, and
the corresponding Wave 3 figure is
`r main("Wave 3 correction effect as a percentage of Wave 1, covariate adjusted")` per cent. No
combination of adjustment, estimator and sample returns 66.4.

Since the sentence names a quantity that four reasonable estimators put between
`r floor(min(persistence_estimates))` and `r ceiling(max(persistence_estimates))` per cent, there
is no single token that can replace 66.4, and the finding is recorded here rather than in the
errata.

### Two further quantities with no counterpart

The appendix states that attitudinal outcomes were observed for 22 political figures and groups.
The deposited data carry `r value("app_fig9_targets")` feeling thermometer columns. And appendix
Table 9 reports a mean adjusted r-squared for each of ten covariates across "our 21 experiments,
resulting in 210 separate linear models"; the deposit ships no code for that table, and the
article elsewhere describes `r value("res_opportunities")` experiments. The rewrite adds no
script for it, since writing one would be estimating something the deposited archive never did.

## The ground truth

`ground_truth/coppock_etal_2023_ground_truth.csv` carries one row per published claim.
`value_paper` is the string the article prints and is the only column anyone typed;
`value_script` is read out of the deposit and `value_rewrite` out of `maintained/output/`, both by
script. A value agrees when the computed number, printed to the page's own precision, gives the
same digits.

```{r}
#| label: gt-summary
#| echo: false
gt |>
  mutate(verdict = case_when(
    !is.na(match_rewrite) & match_rewrite == 1 ~ "reproduces",
    !is.na(match_rewrite) & match_rewrite == 0 ~ "does not reproduce",
    !is.na(holds) & holds ~ "holds",
    !is.na(holds) & !holds ~ "does not hold",
    TRUE ~ "no verdict"
  )) |>
  count(claim_type, verdict) |>
  pivot_wider(names_from = verdict, values_from = n, values_fill = 0) |>
  show_table(caption = "Published claims by type and verdict.")
```

```{r}
#| label: gt-locus
#| echo: false
gt |>
  filter(!is.na(defect_locus)) |>
  count(defect_locus, name = "rows") |>
  show_table(caption = "Where the fault lies, on every row that is not a clean match.")
```

Every row that is not a clean match carries a `defect_locus`, and no clean match carries one. The
five values are `paper_internal` (the article disagrees with its own tables or its own data),
`archive` (the deposit cannot support the claim), `environment` (R or a package moved underneath
it), `rewrite` (ours) and `unresolved` (cause not established).

### Coverage, float by float

```{r}
#| label: coverage
#| echo: false
coverage |>
  select(float, `printed numbers` = printed_numbers, covered = numbers_covered,
         fraction = covered_fraction, `plotted quantities` = plotted_quantities,
         `counts verified` = counts_verified) |>
  show_table(caption = "Coverage per published float. Printed numbers are what a float puts on its own face; plotted quantities are what it draws.")
```

Seven of the appendix's floats and two of the article's print no numbers at all. For those the
checkable published quantity is the count of what they plot, and that count is verified; the
fraction is left empty rather than reported as zero.

Two floats are covered thinly and both are worth stating plainly. **Figure 3 is the largest gap in
this repository.** It labels every effect significantly different from zero and every one of its
eight meta-analytic summaries, roughly `r coverage$printed_numbers[coverage$float == "Figure 3"]`
printed numbers, and none of those labels was transcribed. What is verified is that the figure
plots `r value("fig3_cells")` conditional effect estimates, and that those estimates are the
covariate-adjusted cells of appendix Tables 2 and 3, every one of which reproduces. **Appendix
Table 1** prints 206 numbers, of which the eight panel sizes are checked individually and the
rest are checked as counts of non-empty cells.

The seven appendix regression tables are the bulk of the published record: `r nrow(published_cells)`
cells, each printing an estimate, a standard error and two interval bounds, so
`r nrow(published_cells) * 4` published numbers. All of them are parsed positionally from the
published PDF into `ground_truth/published_appendix_values.csv` and compared cell by cell.

## The extraction and the two instruments

`ground_truth/published_claims.csv` is the extraction: `r nrow(extraction)` rows, one per numeric
claim in the article and its appendix, each classified by hand as `pipeline`, `descriptive`,
`definitional`, `structural` or `transcribed`, and each carrying the string the page prints and
the precision it prints it at. Spelled-out numbers were swept for separately from digits, since
no token scan sees "eight panel experiments", "twelve out of the twenty-four opportunities" or
"thirteen days"; `r sum(str_detect(extraction$location, "\\bone\\b|\\btwo\\b|\\bthree\\b|\\bfour\\b|\\bsix\\b|\\beight\\b|twelve|thirteen|fourteen|twenty|hundred"))`
of the extraction's quoted sentences state their number in words.

Two instruments read the same pipeline output by separate paths.
`ground_truth/build_ground_truth.R` builds the comparison table.
`maintained/in_text_claims.R` carries the article's own sentence in a block comment beside code
that recomputes the number, and prints
`r sum(extraction$needs_block)` claims in the form `CLAIM <id> = <value> || <label>`. It reads
`maintained/output/` and the extraction, never the ground truth, so the two derivations are
independent and a disagreement between them is a finding.

The build asserts all of the following and stops if any fails.

- Every `pipeline` and `descriptive` claim has a block and a row.
- The number of printed claims equals the number of rows requiring one, and the two sets of ids
  are equal in both directions.
- Every value the two instruments both produce agrees exactly.
- Re-rendering `value_paper` from its own number at its own recorded precision returns the string
  the extraction stores, which is what catches a precision that is right about the value and
  wrong about the digits.
- Every adverse row carries a `defect_locus` and no clean match does.
- Every published float has at least one row.

Each of the first, third and fourth was tested by breaking it: deleting a block fails the count,
perturbing a printed value fails the cross-check, and changing one claim's recorded precision
fails the string check.

## The maintained rewrite

`maintained/` is `r length(list.files(here::here("maintained"), pattern = "\\.R$"))` scripts.
`fit_all_models.R` fits every model from the deposited survey data and writes each family as a
tidy CSV under `maintained/output/fits/`, so every number a figure or table prints can be traced
to a file a reader can open. Nothing downstream reads the deposit's saved objects.

The substitutions the rewrite makes are the usual ones for code of this age: the native pipe for
`magrittr`, `pivot_longer`/`pivot_wider` for `reshape2::melt`/`dcast`, `reframe(tidy(...))` for
`do(tidy(...))`, `pick(everything())` for `cur_data()`, `write_csv()` for `xtable` printed to the
console, `linewidth` for the deprecated `size` aesthetic, and `position_dodge()` for
`ggstance::position_dodgev()`. The Roboto font dependency in the traffic figure is dropped.
`plyr` is not loaded at all, which removes the masking hazard the deposit works around by loading
it first.

## Figure verification

Every rendered figure was laid beside the published one. Numbers alone cannot catch a transposed
axis or a mislabelled series, and three of this article's six figures print their estimates on
the face of the plot, which makes them published tables in disguise.

```{r}
#| label: figure-2
#| echo: false
#| fig-cap: "Figure 2 as the rewrite draws it. All seventy-two conditional means reproduce the published labels exactly."
figure("figure_2_raw_outcomes_by_treatment")
```

```{r}
#| label: figure-5
#| echo: false
#| fig-cap: "Figure 5 as the rewrite draws it. Thirty-four of thirty-six labels reproduce; the two political knowledge correction labels move, which is environment drift rather than a defect in either analysis."
figure("figure_5_heterogeneity_by_trait")
```

```{r}
#| label: figure-6
#| echo: false
#| fig-cap: "Figure 6 as the rewrite draws it, with the thermometer models fitted on the panel that carried each claim. All eight labels differ from the published ones."
figure("figure_6_ft_targets")
```

```{r}
#| label: figure-4
#| echo: false
#| fig-cap: "Figure 4 as the rewrite draws it. In the published version the Wave 1 and Wave 2 points of the bottom-left panel sit at the same height, because the deposit fits both on the Wave 3 outcome."
figure("figure_4_persistence")
```

## Rewrite verification

`run_all.R` was run to completion twice from clean sessions and the whole tree diffed. Every CSV
is byte-identical between runs. The figure PDFs differ, because a PDF records the time it was
written.

`original/` is verified twice per run: `download_original.R` is sourced first, which checks every
file against the MD5 Dataverse serves for `?format=original` and against its deposited byte size,
and refuses to continue if `original/` holds any file the manifest does not list, dotfiles
included. It is sourced again as the last step, because the first pass proves only that the
archive was intact when the run began. All `r nrow(manifest)` files match, and
`r sum(manifest$md5_served != manifest$md5_published)` carry a published checksum that disagrees
with the bytes Dataverse serves. Checksums for files this repository writes are not quoted
anywhere: a PDF records its write time, so its hash changes on every run.

## R environment

```{r}
#| label: session
#| echo: false
tibble(
  component = c("R", "tidyverse", "estimatr", "metafor", "ggplot2", "broom"),
  version = c(
    paste(R.version$major, R.version$minor, sep = "."),
    as.character(packageVersion("tidyverse")),
    as.character(packageVersion("estimatr")),
    as.character(packageVersion("metafor")),
    as.character(packageVersion("ggplot2")),
    as.character(packageVersion("broom"))
  )
) |>
  show_table()
```

The rewrite keeps the current sampler and the current packages throughout. Nothing in this
analysis draws at random: no script calls `sample()`, `rnorm()` or a bootstrap, so the results are
bit-identical at any seed and the sampler change in R 3.6 is not in play.
